Consumer extinctions constrain phenotypic evolution in the resulting food web

### 2019-05-19 analyses/reproduce_analyses.Rmd
aesthetic changes. transitioning this into a document where the .html serves as supplementary material.

---
title: "Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*"
author: "Matthew A. Barbour"
date: "`r Sys.Date()`"
output:  
  prettydoc::html_pretty:
    theme: architect
    highlight: github
fontsize: 11pt
---

## Setup

Suppress messages, warnings, and errors for document aesthetics.

```{r setup}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, error=FALSE)
```

Load required libraries.

```{r required libraries, results='hide'}
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(latex2exp)  # using Latex notation for axes labels
library(stringr)
library(MVN)        # assessing multivariate normality assumption
```

Write custom functions to avoid repetitive code.

```{r custom functions}
# Transform logit to probability
inverse_logit <- function(x) exp(x)/(1+exp(x))

@@

Set parameters for analyses and plots.

```{r set parameters}
# Number of bootstrap replicates
n_boots_analysis <- 1000
n_boots_plots <- 100

# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; 
# order: orange, light blue, green, yellow, dark blue, red, pink
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
complex_color <- cbPalette[6] 
simple_color <- cbPalette[5] 
treatment_colors <- c(complex_color, simple_color)
```

Read and tidy data for analyses.

```{r read and tidy data}

@@

# all sources of mortality
mean(full_df$gall_survival) + mean(full_df$egg.ptoid) + mean(full_df$larval.ptoid) + mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)

mean(full_df$gall_survival) # 40% survival
mean(full_df$egg.ptoid) # 26% egg parasitism
mean(full_df$larval.ptoid) # 11% larval parasitism
mean(full_df$early.larval.death) # 17% early larval death
mean(full_df$unknown_mortality) # 7% unknown

@@

## Evaluating assumption of multivariate normality

@@

```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
```

```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
```

@@

## Gall trait-fitness relationships: effect of food-web treatment

@@

```{r Food-web model, cache=TRUE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap food-web model, cache=TRUE}
boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Linear food-web model, cache=TRUE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap linear food-web model, cache=TRUE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Bias in food-web model, cache=TRUE}

@@

```{r biased foodweb table, echo=FALSE}
# Print table
biased_foodweb_confint %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
```

@@

We gather regression coefficients from the full and reduced model to display trait-fitness relationships. For chamber diameter, we subtracted the coefficient due to bias to better approximate the trait-fitness relationship. We also used the bootstrapped samples to calculate the differences in estimates between treatments (labelled **Diff**).

@@

```{r Table of food web coefficients, echo=FALSE}
tidy_foodweb_alphas %>%
  filter(type != "Diff") %>%
  select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
 knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
```

@@

```{r Table of differences in food web coefficients, echo=FALSE}
tidy_foodweb_alphas %>%
  filter(type == "Diff") %>%
  select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
 knitr::kable(., caption = "Table of differences in mean fitness and trait-fitness relationships between food-web treatments.")
```

@@

## Gall trait selection gradients

Using the methods proposed by [Janzen and Stern, 1998](https://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.1998.tb02237.x), we estimated selection gradients from our trait-fitness relationships.

```{r Food-web selection gradients}

@@

foodweb_simple_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebSimple:")) %>%
  transmute_all(funs(foodweb_simple_gradient))

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_grads <- bind_cols(foodweb_complex_raw_gradients, foodweb_simple_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

@@

```{r Table of food web selection gradients, echo=FALSE}
tidy_foodweb_grads %>%
  filter(type != "Diff") %>%
  select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
knitr::kable(., caption = "Table of selection gradients acting on gall traits in each food-web treatment.")
```

@@

```{r Table of differences in selection gradients between food-web treatments, echo=FALSE}
tidy_foodweb_grads %>%
  filter(type == "Diff") %>%
  select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Table of differences in selection gradients acting on gall traits between food-web treatment.")
```

@@

```{r Curvature, echo=FALSE}
# Calculate curvatures for complex food web
foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:I(sc.Diam^2)` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.Diam`,
         `FoodwebComplex:C.Clutch` = `FoodwebComplex:I(sc.log.Clutch^2)` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.log.Clutch`,
         `FoodwebComplex:C.Pref` = `FoodwebComplex:I(sc.sqrt.Pref^2)` - `FoodwebComplex:sc.sqrt.Pref`*`FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.log.Clutch`,
         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.sqrt.Pref`)

@@

```{r Table of food web curvatures, echo=FALSE}
tidy_foodweb_curvs %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
```

@@

```{r Table of differences in curvatures between food-web treatments, echo=FALSE}
tidy_foodweb_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
```

@@

@@

## Gall trait-fitness relationships: contribution of egg and larval parasitoids

@@

```{r Egg vs. larval ptoid model, cache=TRUE}
# excludes cases of egg-parasitism from Complex food web
egglarval_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & egg.ptoid < 1)

@@

```{r Bootstrap egg vs. larval ptoid model, cache=TRUE}
boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Linear egg vs. larval ptoid model, cache=TRUE}
linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
```

@@

```{r Bootstrap linear egg vs. larval model, cache=TRUE}
boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

Tidy trait-fitness relationships for egg and larval parasitoids from above models.

@@

```{r Table of egg vs. larval coefficients, echo=FALSE}
tidy_egglarval_alphas %>%
  filter(type != "Diff") %>%
  select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of gall trait-fitness relationships imposed by egg and larval parasitoids. Note that type = Simple = Egg parasitoid and Complex = Larval parasitoid.")
```

@@

```{r Table of differences in egg vs. larval coefficients, echo=FALSE}
tidy_egglarval_alphas %>%
  filter(type == "Diff") %>%
  select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of differences in gall trait-fitness relationships between egg and larval parasitoids.")
```

@@

## Selection gradients acting on gall traits due to egg and larval parasitoids

```{r Egg vs. larval ptoid selection gradients}

@@

egglarval_simple_raw_gradients <- select(egglarval_adj_Diam, starts_with("FoodwebSimple:")) %>%
  transmute_all(funs(egglarval_simple_gradient))

# Calculate differences between food-web treatments, then estimate means and confidence intervals
egglarval_grads <- bind_cols(egglarval_complex_raw_gradients, egglarval_simple_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

@@

```{r Egg vs. larval selection gradients, echo=FALSE}
tidy_egglarval_grads %>%
  filter(type != "Diff") %>%
  select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
knitr::kable(., caption = "Table of selection gradients imposed by egg and larval parasitoids.")
```

@@

```{r Table of differences in selection gradients between egg and larval parasitoids, echo=FALSE}
tidy_egglarval_grads %>%
  filter(type == "Diff") %>%
  select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Table of differences in selection gradients imposed by egg and larval parasitoids.")
```

@@

Create plots for each panel of Figure 2 in main text.

```{r Plot Univariate Landscapes}
uni_breaks <- c(0.1,0.5,1.0)

>>>>

---
title: "Consumer extinctions constrain phenotypic evolution in the resulting food web"
subtitle: "Supplementary information"
author: "Code author: Matthew A. Barbour"
date: "`r Sys.Date()`"
output: 
  tufte::tufte_html:
    toc: true
#fontsize: 11pt
---

This document presents a hybrid summary of the code used to reproduce these analyses. It is intended to give the reader a higher-level picture of the analyses, but does not display more minor code related to aesthetics. The underlying code for this document is provided in *reproduce_analyses.Rmd* and is available at https://github.com/mabarbour/complexity_selection.

```{r setup, include=FALSE}
# Suppress messages, warnings, and errors for document aesthetics.
knitr::opts_chunk$set(message=FALSE, warning=FALSE, error=FALSE, echo=FALSE, dev="png")
```

```{r required libraries, results='hide'}
# Load required libraries.
library(car)        # for homogeneity of variance test
library(tidyverse)  # for managing data
library(cowplot)    # pretty default ggplots
library(broom)      # for tidying multiple linear models
library(viridis)    # for color palette
library(lme4)       # for generalized linear mixed models
library(latex2exp)  # using Latex notation for axes labels
library(stringr)
library(MVN)        # assessing multivariate normality assumption
```

```{r custom functions}
## Write custom functions to avoid repetitive code.

# Transform logit to probability
inverse_logit <- function(x) exp(x)/(1+exp(x))

@@

Set number of bootstrap replicates for analyses and plots.

```{r set parameters, echo=TRUE}
n_boots_analysis <- 1000
n_boots_plots <- 100
```

```{r color palette}
# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; 
# order: orange, light blue, green, yellow, dark blue, red, pink
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
complex_color <- cbPalette[6] 
simple_color <- cbPalette[5] 
treatment_colors <- c(complex_color, simple_color)
```

```{r read and tidy data}
## Read and tidy data for analyses.

@@

@@

## Multivariate normality of phenotypic traits

@@

@@

```{r Univariate_histograms,  fig.cap="Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
```

```{r Multivariate_QQ, fig.show = 'asis', fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")  
```

## Selection surfaces on gall midges: food-web treatments

@@

```{r Food-web model, cache=TRUE, echo=TRUE}
foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap food-web model, cache=TRUE, echo=TRUE}
boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Linear food-web model, cache=TRUE, echo=TRUE}
linear_foodweb_model <- glmer(
  gall_survival ~ 
    -1 + Foodweb + 
    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
```

@@

```{r Bootstrap linear food-web model, cache=TRUE, echo=TRUE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Bias in food-web model, cache=TRUE, echo=TRUE}

@@

@@

```{r biased foodweb table, echo=FALSE}
# Print table
biased_foodweb_confint %>%
  select(term, estimate, conf.low, conf.high) %>%
  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Estimates of bias in selection surface of chamber diameter in each food-web treatment.")
```

We gather regression coefficients from the full and reduced model to display trait-fitness relationships. For chamber diameter, we subtracted the coefficient due to bias to better approximate the trait-fitness relationship. <!--We also used the bootstrapped samples to calculate the differences in estimates between treatments (labelled **Diff**).-->

@@

```{r Table of food web coefficients}
tidy_foodweb_alphas %>%
  filter(type != "Diff") %>%
  select(Term = term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  mutate(Term = term, Treatment = type, Estimate = round(mean, 3), `2.5%` = round(conf.low, 3), `97.5%` = round(conf.high, 3)) %>%
 knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
```

@@

```{r Table of differences in food web coefficients, include=FALSE}
tidy_foodweb_alphas %>%
  filter(type == "Diff") %>%
  select(Term = term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  mutate(Estimate = round(mean, 3), `2.5%` = round(conf.low, 3), `97.5%` = round(conf.high, 3)) %>%
 knitr::kable(., caption = "Table of differences in mean fitness and selection surfaces between food-web treatments.")
```

@@

## Selection gradients on gall midges: food-web treatments

Using the methods proposed by [Janzen and Stern, 1998](https://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.1998.tb02237.x), we estimated selection gradients from our selection surfaces.

```{r Food-web selection gradients, echo=TRUE}

@@

foodweb_simple_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebSimple:")) %>%
  transmute_all(funs(foodweb_simple_gradient))
```

```{r Tidy up selection gradients}
# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_grads <- bind_cols(foodweb_complex_raw_gradients, foodweb_simple_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

@@

```{r Table of food web selection gradients}
tidy_foodweb_grads %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
knitr::kable(., caption = "Table of selection gradients acting on gall traits in each food-web treatment.")
```

@@

```{r Table of differences in selection gradients between food-web treatments, include=FALSE}
tidy_foodweb_grads %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Table of differences in selection gradients acting on gall traits between food-web treatment.")
```

@@

```{r Curvature, include=FALSE}
# Calculate curvatures for complex food web
foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:I(sc.Diam^2)` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.Diam`,
         `FoodwebComplex:C.Clutch` = `FoodwebComplex:I(sc.log.Clutch^2)` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.log.Clutch`,
         `FoodwebComplex:C.Pref` = `FoodwebComplex:I(sc.sqrt.Pref^2)` - `FoodwebComplex:sc.sqrt.Pref`*`FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.log.Clutch`,
         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.sqrt.Pref`)

@@

```{r Table of food web curvatures, include=FALSE}
tidy_foodweb_curvs %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high, P_cutoff) %>% 
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
```

@@

```{r Table of differences in curvatures between food-web treatments, include=FALSE}
tidy_foodweb_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
```

@@

plot_grid(y_title_foodweb_grads, plot_legend_foodweb_grads, ncol=2, rel_widths = c(0.05,1))

@@

## Selection surfaces on gall midges: egg vs. larval parasitoids

@@

```{r Egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
# excludes cases of egg-parasitism from Complex food web
egglarval_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & egg.ptoid < 1)

@@

```{r Bootstrap egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Linear egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
```

@@

```{r Bootstrap linear egg vs. larval model, cache=TRUE, echo=TRUE}
boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

Tidy selection surfaces imposed by egg and larval parasitoids from above models.

@@

```{r Table of egg vs. larval coefficients}
tidy_egglarval_alphas %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of gall selection surfaces imposed by egg and larval parasitoids. Note that type = Simple = Egg parasitoid and Complex = Larval parasitoid.")
```

@@

```{r Table of differences in egg vs. larval coefficients, include=FALSE}
tidy_egglarval_alphas %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of differences in gall trait-fitness relationships between egg and larval parasitoids.")
```

@@

## Selection gradients on gall midges: egg vs. larval parasitoids

```{r Egg vs. larval ptoid selection gradients, echo=TRUE}

@@

egglarval_simple_raw_gradients <- select(egglarval_adj_Diam, starts_with("FoodwebSimple:")) %>%
  transmute_all(funs(egglarval_simple_gradient))
```

```{r Tidy egg vs. larval ptoid selection gradients}
# Calculate differences between food-web treatments, then estimate means and confidence intervals
egglarval_grads <- bind_cols(egglarval_complex_raw_gradients, egglarval_simple_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

@@

```{r Egg vs. larval selection gradients}
tidy_egglarval_grads %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
knitr::kable(., caption = "Table of selection gradients imposed by egg and larval parasitoids.")
```

@@

```{r Table of differences in selection gradients between egg and larval parasitoids, include=FALSE}
tidy_egglarval_grads %>%
  filter(type == "Diff") %>%
  select(term, gradient_type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Table of differences in selection gradients imposed by egg and larval parasitoids.")
```

@@

```{r Plot Univariate Landscapes}
## Create plots for each panel of Figure 2 in main text.

uni_breaks <- c(0.1,0.5,1.0)
